

\chapter{Installation Guide}
%\addcontentsline{toc}{chapter}{Installation Guide}
%\markboth{Installation Guide}{Installation Guide}

The $SimHPN$ toolbox has been developed in the GISED research group (Group of Discrete Event Systems Engineering, \textbf{URL:} \url{http://webdiis.unizar.es/GISED/}), University of Zaragoza, Spain.  It offers a collection of tools devoted to simulation, analysis and synthesis of dynamical systems modeled by hybrid Petri nets. Its embedding in the 
MATLAB environment provides the considerable advantage  of creating powerful algebraic, statistical and graphical 
instruments exploiting the high quality routines available in MATLAB.

$SimHPN$ is a commercial software product for scientific purposes. Its demo version can be freely downloaded from: 

\textbf{URL:} \url{http://webdiis.unizar.es/GISED/?q=tool/simhpn}

If you want to have access to the full version, please contact us at: \url{simhpn@unizar.es}

$SimHPN$ runs on the MATLAB environment and the full version works, in principle, in any operating system that supports MATLAB R2008 or superior. Anyway, the demo version that can be downloaded from the previous link has been compiled on a particular version of MATLAB. If you experience problems in running it please contact us by email.

To install the toolbox, unzip the contents of the archive \textbf{SimHPN\_P.zip} under a folder of your choice. This operation will create the directory $SimHPN$ in the folder you chose. Launch the MATLAB, change the working directory to the folder $SimHPN$ and type 

\texttt{>> SimHPN}

at the MATLAB prompt. The $SimHPN$ GUI will become operational.


\newpage
